---
title: "Import - Edge angle analysis"
author: "Lisa Schunk"
date: "`r Sys.time()`"
output: word_document
---

```{r Knitr Options, include = FALSE}
knitr::opts_chunk$set(comment = NA, message = FALSE, indent = "", error = TRUE)

```


---

# Goal of the script
This script imports and merges all single CSV-files generated with the 'edge angle method'. The data derives from 3D models of artefacts from the three sites Balver Höhle, Buhlen and Ramioul.  
The script will:

1. Read in the original CSV-files   
2. Combine the data from all samples into one 
3. Write an XLSX-file and save an R object ready for further analysis in R 



```{r}
dir_in <- "analysis/raw_data"
dir_out <- "analysis/derived_data/"

```


Raw data must be located in "`r dir_in`".  
Formatted data will be saved in "`r dir_out`".
The knit directory for this script is the project directory.

---


# Load packages
```{r}
library(tidyverse)
library(R.utils)
library(openxlsx)
library(tools)

```


---


# List all files and get names of the files  
```{r}
# List all CSV files in dir_in
CSV_files <- list.files(dir_in, pattern = "\\.csv$", recursive = TRUE, full.names = TRUE)

```



# Merge all files and format the data 
```{r}
# Create a list 
data_final <- vector(mode = "list", length = length(CSV_files)) 
names(data_final) <- basename(CSV_files)

# For each sample
for (s in seq_along(data_final)) {
  
    # Gets sample ID from path names 
    ID <- dirname(dirname(dirname(CSV_files[s]))) %>%
          basename()

    # Gets name of the site from path names 
    site <- basename(dirname(dirname(dirname(dirname(dirname(CSV_files[s])))))) %>% 
            gsub("([A-Za-z0-9_]*-)", "", x = .)
    
    # Gets tool type from path names 
    tool_type <- dirname(dirname(dirname(dirname(CSV_files[s])))) %>%
          basename() 
    
    # Gets section from path names
    sec <- basename(CSV_files[s]) %>%
      gsub("^[A-Za-z0-9_-]*_SEC-", "", x = .) %>% 
      gsub("_.*\\.csv$", "", x = .) %>% 
      as.numeric()
    
    # Gets edge (E1/E2/E3) from path name
    edge <- basename((dirname(CSV_files[s])))
    edge <- unlist(strsplit(edge, "_"))[3]  
       
    
  # read the data files
  data_final[[s]] <- read.csv(CSV_files[s]) %>% 
                     mutate(Site = site, ID = ID, Tool_type = tool_type, Section = sec, 
                     Edge = edge) %>% 
                     select(Site, ID, Tool_type, Section, Edge, everything()) %>% 
                     select(-section) %>%
                     rename(Angle_number = angel_number, 
                            Distance_origin = dist.to.origin.on.curve..mm., 
                            Segment = segment.on.section..mm.,
                            Three_point = angle.1..3.points...degree., 
                            Two_lines = angle.2..2.constructed.lines...degree., 
                            Best_fit = angle.3..2.BestFit.lines...degree.)
}

# rbind all files 
data_final <- do.call(rbind, data_final)
# adds indices as row names 
row.names(data_final) <- 1:nrow(data_final)

```



# Save data
## Format name of output file
```{r}
file_out <- "EdgeAngle"

```


## Write to XLSX
```{r}
write.xlsx(list(data = data_final), file = paste0(dir_out, file_out, ".xlsx")) 

```


## Save R object
```{r}
saveObject(data_final, file = paste0(dir_out, file_out, ".Rbin"))

```


## Show files information
```{r}
files_out <- list.files(dir_out, full.names = TRUE)
md5_out <- md5sum(files_out)
info_out <- data.frame(files = basename(names(md5_out)), checksum = md5_out, 
                       row.names = NULL)

```

The checksum (MD5 hashes) of the exported files are:  
```{r, echo = FALSE}
info_out

```


---

# sessionInfo() and RStudio version

```{r}
sessionInfo()

```

RStudio version `r readLines("analysis/scripts/RStudioVersion.txt", n = 1)`.


---


END OF SCRIPT
